---
title: "graphhighlight"
author: "Noriaki Sato"
date: "2023-03-27"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{graphhighlight}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      fig.width=8,
                      fig.height=8,
                      warning=FALSE,
                      message=FALSE)
```

# graphhighlight

This package highlights nodes, edges and node texts of ggraph plots when one wants to inspect the graph information after the plots are created.

## Usage

Generate a random graph.

```{r gen, message=FALSE, warning=FALSE}
library(ggraph)
library(igraph)
library(graphhighlight)

set.seed(1)
g <- random.graph.game(10,0.1,directed=TRUE)
E(g)$weight <- sample(1:10, length(E(g)), replace=TRUE)
V(g)$size <- sample(1:10, length(V(g)), replace=TRUE)
V(g)$name <- letters[1:length(V(g))]
```

### highlight_node

This function highlights the nodes by specifying `node_name` or `filter` specifying conditions for including nodes in string. If `highlight_color` is specified, the node color will be changed.

```{r node1}
ggraph(g, layout="nicely")+
  geom_node_point(aes(size=size))+
  highlight_node(filter="size>7",
                 highlight_color="red")+
  theme_graph()
```

Or highlighting by some shapes by stacking the layers.
`highlight_by_shape` specifies highlighting by shape is to be used, and `specify_shape` the shape, `specify_shape_size` the size, `shape_color` the color of the shape.

```{r node2}
ggraph(g, layout="nicely")+
  geom_node_point(aes(size=size))+
  highlight_node(filter="size>7",
                 highlight_by_shape = TRUE,
                 shape_number = 21,
                 shape_size = 21,
                 shape_color="red")+
  theme_graph()
```

Or by making nodes glowing-look. The argument `glow` should be set to `TRUE`.
If no `highlight_color` is specified, the raw colors of nodes are used.

```{r node3}
ggraph(g, layout="nicely")+
  geom_node_point(aes(size=size, color=size))+
  scale_color_viridis()+
  highlight_node(filter="size>7",glow=TRUE)+
  theme_graph()
```
If `highlight_color` is specified and `glow_fixed_color` is `TRUE`, that color is used.

```{r node4}
ggraph(g, layout="nicely")+
  geom_node_point(aes(size=size, color=size))+
  scale_color_viridis()+
  highlight_node(filter="size>7",glow=TRUE,
                 highlight_color="tomato",
                 glow_fixed_color=TRUE)+
  theme_graph()
```

`glow_size` controls how big the glowing will be. `glow_base_size` will use base node size for glowing. Otherwise the same parameters are used for stacking the layers.

```{r node5}
ggraph(g, layout="nicely")+
  geom_node_point(aes(size=size, color=size))+
  scale_color_viridis()+
  highlight_node(filter="size<7",glow=TRUE,
                 glow_size=5,
                 glow_base_size = TRUE)+
  theme_graph()
```

The same glowing function is implemented for highlighting edges in `highlight_edge`, but not for `highlight_node_text` as for the text, `shadowtext` by Prof. Guangchuang Yu implmented in `geom_node_text` and `geom_text_repel` can highlight the text much better.

### highlight_edge

Edges can be highlighted in the same way as `highlight_node`.

```{r edge1, warning=FALSE}
ggraph(g, layout="nicely")+
  geom_edge_diagonal(aes(width=weight,
                         color=weight))+
  scale_edge_color_gradient(low="blue",high="red")+
  highlight_edge(filter="weight>7",
                 highlight_color="pink")+
  theme_graph()
```

The same can be performed for the other geoms.

```{r edge2, warning=FALSE}
ggraph(g, layout="nicely")+
  geom_edge_bend2(aes(width=weight,
                         color=weight))+
  scale_edge_color_gradient(low="blue",high="red")+
  highlight_edge(filter="weight>7",
                 highlight_color="pink")+
  theme_graph()
```

With the arrows.

```{r edge3, warning=FALSE}

ggraph(g, layout="nicely")+
  geom_edge_link(aes(width=weight),
              arrow = arrow(length = unit(4, 'mm')), 
              end_cap = circle(5, 'mm'),
              start_cap = circle(5, "mm"))+
  highlight_edge(filter="weight<5",
                 highlight_color="steelblue")+
  theme_graph()

```

Glowing function can be applied by specifying `glow` to `TRUE`. `geom_edge_size` controls how big the glowing will be. Note that specifying big number will deteriorate the looking.

```{r edge4, warning=FALSE}

ggraph(g, layout="nicely")+
  geom_edge_link(aes(width=weight),
              arrow = arrow(length = unit(4, 'mm')), 
              end_cap = circle(5, 'mm'),
              start_cap = circle(5, "mm"))+
  highlight_edge(filter="weight<5",
                 glow=TRUE,
                 highlight_color="steelblue",
                 glow_edge_size =0.5,
                 glow_fixed_color = TRUE,
                 glow_base_size =TRUE )+
  theme_graph()
```

Coloring of edge labels is controlled by `change_label_color`.

```{r edge5, warning=FALSE}
ggraph(g, layout="nicely")+
  geom_edge_link(aes(width=weight,
                     label=weight),
              angle_calc="along",
              label_dodge = unit(5, 'mm'),
              position="identity",
              arrow = arrow(length = unit(4, 'mm')), 
              end_cap = circle(5, 'mm'),
              start_cap = circle(5, "mm"))+
  highlight_edge(filter="weight>5",
                 change_label_color=TRUE,
                 highlight_color="red")+
  theme_graph()
```

### highlight_node_text

```{r text1}
ggraph(g, layout="nicely")+
  geom_node_text(aes(label=name, color=size, size=size), repel=TRUE, bg.colour="grey")+
  highlight_node_text(filter="size>6",highlight_color = "red")+
  theme_graph()
```

### highlight_node_label

```{r label1}
ggraph(g, layout="nicely")+
  geom_node_label(aes(label=name, color=size), repel=TRUE)+
  highlight_node_label(filter="size>5",highlight_color = "red", highlight_bg_color = "yellow")+
  theme_graph()
```


### Combine

```{r combine}
g <- random.graph.game(100,0.05,directed=FALSE)
E(g)$weight <- sample(1:10, length(E(g)), replace=TRUE)
V(g)$size <- sample(1:10, length(V(g)), replace=TRUE)
V(g)$size <- sample(1:10, length(V(g)), replace=TRUE)

ggraph(g, layout="circle") +
  geom_node_point(aes(size=size, color=size))+
  scale_color_viridis()+
  geom_edge_diagonal(aes(color=weight))+
  scale_edge_color_viridis(guide="none")+
  highlight_node(filter="size>0",glow=TRUE,glow_base_size = TRUE)+
  highlight_edge(filter="weight>0",glow=TRUE,glow_base_size = TRUE)+
  theme_graph()
```


```{r}
sessionInfo()
```